MSSM-Penn-Pitt - ACC and DLPFC - DREAM - FEATURECOUNTS - GRCh38 - CQN - Model Selection

### 2020-04-16 cmc-rnaseq-de/MSSM-Penn-Pitt_ACC_DLPFC_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd
categorical variables as random effects

# Stepwise regression
phase1 <- mvBIC::mvForwardStepwise(exprObj = subset_CQN,
                         baseFormula = base_formula, 
                         data = COVARIATES,
                         variables = array(c("(1|Institution)", "Reported_Gender", "PMI", 
                                                             "ageOfDeath", "RIN", "RIN2", "EV.1", 
                                                             "EV.2", "EV.3", "EV.4", "EV.5")))
phase1
```

@@

#### Phase III (RNASeq alignment specific covariates)
```{r phase3}
phase3 <- mvBIC::mvForwardStepwise(exprObj = subset_CQN,
                         baseFormula = phase2$formula, 
                         data = COVARIATES,
                         variables = array(c("MappedReads", "IntragenicRate", "IntronicRate", "IntergenicRate", "GenesDetected", "rRNARate", "TotalReads")))
phase3
```

>>>>

# Stepwise regression
phase1 <- mvBIC::mvForwardStepwise(exprObj = subset_CQN,
                         baseFormula = base_formula, 
                         data = COVARIATES,
                         variables = array(c("(1|Institution)", "(1|Reported_Gender)", "PMI", 
                                                             "ageOfDeath", "RIN", "RIN2", "EV.1", 
                                                             "EV.2", "EV.3", "EV.4", "EV.5")))
phase1
```

@@

#### Phase III (RNASeq alignment specific covariates)
```{r phase3}
phase3 <- mvBIC::mvForwardStepwise(exprObj = subset_CQN,
                         baseFormula = phase2$formula, 
                         data = COVARIATES,
                         variables = array(c("IntragenicRate", "IntronicRate","IntergenicRate","rRNARate", "TotalReads", "GenesDetected", "MappedReads")))
phase3
```
